Exp. 2 Analysis: 2AFC, adults vs. children

### 2020-09-01 analysis/exp2_analysis.Rmd
more prelim model data from Michael, updating children's drop data

```{r load-model-data, include=F}
mdat <- read_csv("agent-data/curiodrop-model-8-23-20.csv")

@@

mdat %>% group_by(drop, target, train_stage) %>% # alt, 
  summarize(chose_target=mean(chose_target), n=n()) %>%
  ggplot(aes(x=train_stage, y=chose_target, group=target, color=target)) + 
  facet_wrap(.~ drop) + 
  geom_point(aes(size=n)) + geom_line() + theme_bw() + ylim(0,1)

mdat %>% distinct(drop, target, alt)
```

@@

cd <- rawch %>% filter(Exclude!="Y") %>% 
  dplyr::select(-Version, -Torus0, -Exclude, -Qual1, -Qual2, -Notes)

@@

>>>>

```{r load-model-data, include=F}
mdat <- read_csv("agent-data/curiodrop-model-8-23-20.csv")
mdat <- read_csv("agent-data/curiodrop_0.csv") # most trials close to chance
mdat <- read_csv("agent-data/curiodrop_1.csv")
mdat <- read_csv("agent-data/curiodrop_2.csv")

@@

mdat %>% group_by(drop, target) %>% # alt, 
  summarize(chose_target=mean(chose_target), n=n())

mdat %>% group_by(drop, target, train_stage) %>% # alt, 
  summarize(chose_target=mean(chose_target), n=n()) %>% 
  ggplot(aes(x=train_stage, y=chose_target, group=target, color=target)) + 
  facet_wrap(.~ drop) + 
  geom_point(aes(size=n)) + geom_line() + theme_bw() + ylim(0,1) + 
  geom_hline(aes(yintercept=.5), linetype="dashed")

#mdat %>% distinct(drop, target, alt)
```

@@

cd <- rawch %>% filter(Exclude!="Y") %>% 
  dplyr::select(-Version, -Torus0, -Exclude, -Qual1, -Qual2, -Notes, -Note)

@@

# Octahedron   39  p= 0.003
#   pyramid trig prism 
#      0.74       0.26 
# Pentagon   41  p= 0.001
#    bowl pentagon 
#    0.76     0.24 
# Pyramid   41  p= 0.06
# octahedron      torus 
#      0.34       0.66 
# Dumbbell_1   42  p= 0.02
#      bowl octahedron 
#      0.69       0.31 
```
